---
title       : Life Expectancy at Birth by Country
subtitle    : One aspect of inequality in the world
author      : Shoko Sakamoto
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]    # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What is 'Life Expectancy at Birth'(LEB)?

Life expectancy at birth indicates the number of years a newborn infant would live if prevailing patterns of mortality at the time of its birth were to stay the same throughout its life.[Source](http://data.worldbank.org/indicator/SP.DYN.LE00.IN)

- In most countries **LEB** has increased in past 50 years.
- There are few countries Where **LEB** has not increased at all.
- By applying Liner Regression Model, the coefficient of model shows the increase ratio of **LEB** per year.

## Top and bottom countries of LEB 
- Download data from [Source](http://data.worldbank.org/indicator/SP.DYN.LE00.IN)
```{r reg1, echo=FALSE, results='hide',fig.width=10, fig.height=5}
LeData2 <-  read.csv("C:\\Users\\Shoko\\Documents\\R\\project\\LifeExpectancy.csv", header=TRUE, na.strings=c(''))
```
- Apply Liner Regression Model to each country. Rank countries by coefficient.
- Rank countries by the latest data

--- .class #id
Calculate each country's coefficient from Liner Regression and store latest LED
```{r reg2, echo=TRUE, results='show'}
lmdata <- function (country) {
  x <- substr(names(LeData2),2,5)[3:55]; y <- LeData2[LeData2[1]==country][3:55]
  data <- data.frame(cbind(as.numeric(x), as.numeric(y))); names(data) <- c('X1', 'X2');data
}
df = data.frame(matrix(vector(), 0, 3, dimnames=list(c(), c("country", "slope","latest"))), stringsAsFactors=F)
for(i in 1:nrow(LeData2)) {
  cdata <- lmdata(as.character(LeData2[i,1])) 
  df[i,2] <- lm(X2 ~ X1, data=cdata)$coeff[2];df[i,1] <- as.character(LeData2[i,1])
  df[i,3] <- cdata[nrow(cdata),2]
} 
```
Bottom coefficient
```{r reg3, echo=TRUE, results='show'}
head(df[order(df$slope),],5)
```

--- .class #id
Top coefficient
```{r reg4, echo=TRUE, results='show'}
head(df[order(-df$slope),],5)
```
Bottom LED in 2012
```{r reg5, echo=TRUE, results='show'}
head(df[order(df$latest),],5)
```

--- .class #id
Top LED in 2012
```{r reg6, echo=TRUE, results='show'}
head(df[order(-df$latest),],5)
```

## Interactive comparison of **LEB** between two countries 
- [https://shokoskmt.shinyapps.io/project/](https://shokoskmt.shinyapps.io/project/)
- Check the differnce of **LEB** trend between two countries you concern.
- See the actual past **LEB** and predicted **LEB** (2013~)
